PK object batch mode trial

### 2023-06-20 data-raw/batchMode_trial_gpm.Rmd
Updated residuals() method, ensured predict() method was responsive to use_scale_conc argument for rmse() and residuals().

```{r single_fit}
my_pk <- pk(data = my_predata) +
  facet_data(vars(Chemical, Species)) +
  settings_preprocess(keep_data_original = TRUE) +
  settings_optimx(method = c("L-BFGS-B", "bobyqa")) +
  scale_conc(dose_norm = TRUE) +
  # scale_time() +
  # stat_model() + 
  stat_error_model(error_group = vars(Chemical, Species, Reference))

@@

my_coefs_update <- coef(my_pk)
my_pred_update <- predict(my_pk,
                          exclude = TRUE, # add the "exclude" column to output
                          use_scale_conc = TRUE)

@@

rmse(my_pk) %>% View("RMSE_test")

@@

```{r remaining_methods}
# rmse()
# get_tkstats()
# residuals()
# plot()

>>>>

```{r single_fit}
my_pk <- pk(data = my_predata) +
  facet_data(vars(Chemical, Species)) +
  settings_preprocess(keep_data_original = TRUE) +
  settings_optimx(method = c("L-BFGS-B", "bobyqa")) +
  scale_conc(dose_norm = TRUE, log10_trans = FALSE) +
  # scale_time() +
  # stat_model() + 
  stat_error_model(error_group = vars(Chemical, Species, Reference))

@@

my_coefs_update <- coef(my_pk)
my_pred_update <- predict(my_pk,
                          exclude = TRUE, # add the "exclude" column to output
                          use_scale_conc = FALSE)

@@

rmse(my_pk) %>% View("RMSE_test")
residuals(my_pk) %>% View("Residuals_test")

@@

```{r remaining_methods}
# residuals()
# plot()
# 
# get_tkstats()
